Bird beak's elaboration and exploration: data preparation

### 2022-11-09 Analysis/01-Data_preparation.Rmd
Update 01-Data_preparation.Rmd

<!-- Compilation time: 30 minutes -->

All the custom code and custom functions called in this document can be downloaded and installed in `R`.

```{r packages_install, eval = FALSE}
## Optional - this snippet installs all the packages required to run the analyses
install.packages(c("devtools", "dispRity", "MCMCglmm", "xtable", "knitr", "ggplot2"))
devtools::install_github("TGuillerme/mcmcmcglmmm")

>>>>

The following script takes around 5-10 minutes to compile. All the custom code and custom functions called in this document can be downloaded and installed in `R`.

```{r packages_install, eval = FALSE}
## Optional - this snippet installs all the packages required to run the analyses
install.packages(c("devtools", "dispRity", "MCMCglmm", "xtable", "knitr", "ggplot2", "patchwork", "tidyverse"))
devtools::install_github("TGuillerme/mcmcmcglmmm")
